%%============
%%  ** Author: Shepherd Qirong
%%  ** Date: 2019-08-19 20:32:26
%%  ** Github: https://github.com/ShepherdQR
%%  ** LastEditors: Shepherd Qirong
%%  ** LastEditTime: 2022-04-10 10:51:45
%%  ** Copyright (c) 2019--20xx Shepherd Qirong. All rights reserved.
%%============
\documentclass[UTF8]{book}
\usepackage{ctex}
\usepackage{multirow,booktabs}
\usepackage{amsmath,amsthm,amsfonts,amssymb,bm,mathrsfs,upgreek,chemarrow} 
\usepackage[paper=a4paper,top=3.5cm,bottom=2.5cm,
left=2.7cm,right=2.7cm,
headheight=1.0cm,footskip=0.7cm]{geometry}
\usepackage{color, graphicx, verbatim}
\RequirePackage{setspace}%%行间距
\setstretch{1.523}

\DeclareMathOperator{\rank}{rank}

\DeclareMathOperator{\sgn}{sgn}



\begin{document}

\title{Computer Vision}
\date{Created on 20190819.\\   Last modified on \today.}
\maketitle


\tableofcontents

%\mainmatter

\chapter{Methodology}

Computer Graphics, from image to model.机器视觉，需要猜测，包括理解、意义。

Computer Vision, from model(modeling, simulation) to image, 计算机图形学，不需要猜测。


\section{Introduction}
    寒武纪物种爆发，因为眼睛的出现
    computer vision begins with Larry Robert,1963. the edges define the shape, 1966 mit AI group established. 
    David Marr book < vision >
    视觉是简单的形状开始的，视觉是分层的
    视觉识别模型：1）Generalized Cylinder 简单物体组成Brooks 1979; 2）Pictorial Structure, 基础元素之间用弹簧连接。
    语义分割：Normalized Cut， shi 1997
    viola jones face detector
    detection ，pascal imagenet，
    sigmoid 换成relu，使得2012比赛冠军，和LeCun1998年的手写数字没有太大区别

\section{Others}
    
    
\subsection{图片分类}
    最近邻算法：L1 distance , 曼哈顿距离，
    \begin{equation}
        d_1=\sum \lvert I_1^i -I_2^i \lvert
    \end{equation}
    特点：每一个测试图片的计算时间是恒定的；Flann是实例库
    L2 distance，l1距离的平方根
    K nearest neighbor， k是超参数
    train data分子集比较超参数，cross-validation 
    线性分类器，需要识别纹理，对无纹理的识别困难
    the threshold at zero \\(max(0,-)\\) function is often called the **hinge loss**. \\
    $
    L_i = \sum_{j\neq y_i} \max(0, s_j - s_{y_i} + \Delta)
    $\\
    初始w为0时，损失等于类数量-1
    **regularization loss**\\
    \begin{equation}
        %\label{11}
        L =  \underbrace{ \frac{1}{N} \sum_i L_i }_\text{data loss} + \underbrace{ \lambda R(W) }_\text{regularization loss}
    \end{equation}

    \begin{equation}
        %\label{22}
        L = \frac{1}{N} \sum_i \sum_{j\neq y_i} \left[ \max(0, f(x_i; W)_j - f(x_i; W)_{y_i} + \Delta) \right] + \lambda \sum_k\sum_l W_{k,l}^2
    \end{equation}
     
%

    weight regularization:
    L2:$\sum W^2$\\
    L1:$\sum |W|$\\
    elastic net $\sum \alpha W^2+|W|$
    max norm regularization
    dropout 



\chapter{Computer Graphics}



\begin{table}[htbp]
    \newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end
    {tabular}}
    \centering
      \caption{Usage of Computer Graphics }
      \label{tab:label}
        \begin{tabular}{cc}
        \toprule
        Name & Notes\\
        \midrule

        Video games & 全局光照，越亮游戏画面越好\\
        movies & 特效。远离现实的较容易。日常见的想要特效看得真实较为困难\\
        animations &zootopia中的动物头发。\\
        Design & Autodesk.Ikea, render\\
        Visualization  &science, engineering, medicine, journalism, etc.\\
        VR, AR.&\\
        Digital Illustration.&\\
        Simulation & dust bowl, black hole.\\
        Graphical User Interfaces.&\\
        Topography.& The quick brown fox jumps over the lazy dog.\\

        \bottomrule
        \end{tabular}
\end{table}


physics of lighting and shading

representing and operating shapes in 3D.



\section{Rasterization}
Project geometry primitives(3D triangles or polygons) into fragments(pixels).



\section{Curves and Meshes}


\section{Ray Tracing}
Shoot rays from the camera though each pixel.

\section{Animation and Simulation}













\end{document}


